### 2022-06-07 src/text/2-package.tex
Address more comments

% This might not be the bast place compared to introduction
The data processing workflow in Gamma-ray astronomy is usually split in two sequences.
The first one deals with the data processing from camera measurement, calibration, event
reconstruction and selection to yield a list of reconstructed gamma-ray event candidates.
This sequence, sometimes referred to as low-level analysis, is usually very specific to
a given observation technique if not a given instrument.

@@

The next step of the analysis is the data reduction on a user-defined geometry.
A typical geometry consists in a spectral representation with a measured
energy axis, and in a spatial representation, either a coordinates system  with a projection
(for 3-dimensional or cube analysis) or a region on the sky (for regular spectral analysis).
The gammapy.maps subpackage provides general multidimensional geometry objects
(Geom) and the associated data structures (Maps), see \ref{ssec:gammapy-maps}.

All observation events and instrument responses are projected onto the
target geometry. Because residual hadronic background models can be subject
to significant uncertainties background correction must be applied,
such as the ring or the fied-of-view background techniques or
background measurements must be performed within, e.g. reflected regions~\citep{Berge07}.
Parts of the data with high associated IRF systematics must also be excluded by defining
a "safe" data range. These data reduction steps are performed by classes and functions
implemented in the gammapy.makers subpackage (see \ref{ssec:gammapy-makers}).

@@

The next step is then typically to model and fit the datasets, either
individually, or in a joint likelihood analysis. For this purpose Gammapy
provides a uniform interface to multiple fitting backends. It also provides
a variety of :ref:`built in models <model-gallery>`. This includes spectral,
spatial and temporal model classes to describe the gamma-ray emission in the sky.
Independently or subsequently to the global modelling, the data can be
re-grouped to compute flux points, light curves and flux as well as significance
maps in energy bands.

>>>>

% This might not be the bast place compared to introduction
The data processing workflow in Gamma-ray astronomy is usually split in two sequences.
The first one deals with the data processing from camera measurement, calibration, event
reconstruction and selection to yield a list of reconstructed gamma-ray event candidates.
This sequence, sometimes referred to as low-level analysis, is usually very specific to
a given observation technique and even to a given instrument.

@@

The next step of the analysis is the data reduction where all observation events and instrument
responses are projected onto a user-defined geometry.A typical geometry consists in a spectral representation with a measured
energy axis, and in a spatial representation, either a coordinates system  with a projection
(for 3-dimensional or cube analysis) or a region on the sky (for regular spectral analysis).
The gammapy.maps subpackage provides general multidimensional geometry objects
(Geom) and the associated data structures (Maps), see \ref{ssec:gammapy-maps}.

All observation events and instrument responses are projected onto the
user defined geometry. Because residual hadronic background models can be subject
to significant uncertainties, background correction must be applied,
such as the ring or the field-of-view background techniques or
background measurements must be performed within, e.g. reflected regions~\citep{Berge07}.
Parts of the data with high associated IRF systematics must also be excluded by defining
a "safe" data range. These data reduction steps are performed by classes and functions
implemented in the gammapy.makers subpackage (see \ref{ssec:gammapy-makers}).

@@

The next step is then typically to model and fit the datasets, either
individually, or in a joint likelihood analysis. For this purpose Gammapy
provides a uniform interface to multiple fitting backends. It also provides
a variety of :ref:`built in models <model-gallery>`. This includes spectral,
spatial and temporal model classes to describe the gamma-ray emission in the sky.
Where spectral models can be simple analytical models or more complex ones from radiation
mechanisms of accelerated particle populations (e.g. inverse Compton or $\pi^{o}$ decay).
Independently or subsequently to the global modelling, the data can be
re-grouped to compute flux points, light curves and flux as well as significance
maps in energy bands.
